### 2019-04-08 papers/journal/encoding.tex
Todos till experiments done

%if all the pairs of the present molecule are present on the same edge than all of them inhibit each other resulting in making all the molecules inactive, we term this process ``pairing inhibition".
%
The constraints for the variants can be given to a SAT or a SMT solver to find
VTSs that belong to the variants.
\subsection{Encoding for $\fqbf$ search problem}\label{enc:univ-cond}
%
\input{satqbf-table}
\noindent The specification for universal condition~\ref{sec:property} requires quantifier alternation. 
%
Most SAT solvers can not efficiently handle the quantifier in the formulas. 
% 
Although, it is possible to encode the universal condition as a SAT or SMT problem.
%
There is always a danger of a blow-up in the formula size, making it harder for the SAT solver to handle. 
%Which may blow up the formula size for the solver to solve.
% 
As an experiment, we have implemented a direct SMT version (encoding not presented) of the universal problem extending the current $\fsmt$ search encodings.
%
The basic idea is to conjunct the formula for each combination value of the quantified variable. 
%
The Table~\ref{tab:satqbf-graph}, shows the search results of this encoding for the universal condition with 4 nodes and 3-connected graphs. 
%
The connectivity constraint and connectedness constraints are tagged with subscript $U$, $\texttt{StabilityC}_{U}$, $\texttt{Connected}(k)_{U}$,  to distinguish from earlier presented encodings of existential condition.
%
The SMT extended version was not able to scale it to the desired results and either timed-out (T/O) or ran out of memory (M/O).
%
This can be due to the fact that directly translating a quantified formula into a quantifier-free by introducing a vector of variables for each boolean possibility \change{Increase the formula size exponentially.. the current statement is a repeat of the forth line. Improve.}will blow up the size of the formula and may not be solvable by a solver.
%
%
\subsubsection{$\fqbf$ search encoding of the universal condition}
We will describe several constraints that encode universal condition based on QBF formulation in this section.
%
To avoid cumbersome notation, we will not explicitly write the ranges
of the indexing in the constraints.
%
$i$ and $j$ will range over nodes, i.e., from $1$ to $\nu$.
%
$m$ will range over molecules, i.e., from $1$ to $\mu$.
%
$q$ will range over edges between two nodes, i.e., from $1$ to $\pi$.
%

>>>>

%if all the pairs of the present molecule are present on the same edge than all of them inhibit each other resulting in making all the molecules inactive, we term this process ``pairing inhibition".
%
The constraints for the variants can be given to a SAT or a SMT solver to find
VTSs that belong to the variants.
\subsection{Encoding for $\fqbf$ search problem}\label{enc:univ-cond}
%
\input{satqbf-table}
\noindent The specification for universal condition~\ref{sec:property} requires quantifier alternation. 
%
Most SAT solvers can not efficiently handle the quantifier in the formulas. 
% 
Although, it is possible to encode the universal condition as a SAT or SMT problem.
%
There is always a danger of a blow-up in the formula size, making it harder for the SAT solver to handle. 
%Which may blow up the formula size for the solver to solve.
% 
As an experiment, we have implemented a direct SMT version (encoding not presented) of the universal problem extending the current $\fsmt$ search encodings.
%
The basic idea is to conjunct the formula for each combination value of the quantified variable. 
%
The Table~\ref{tab:satqbf-graph}, shows the search results of this encoding for the universal condition with 4 nodes and 3-connected graphs. 
%
The connectivity constraint and connectedness constraints are tagged with subscript $U$, $\texttt{StabilityC}_{U}$, $\texttt{Connected}(k)_{U}$,  to distinguish from earlier presented encodings of existential condition.
%
The SMT extended version was not able to scale it to the desired results and either timed-out (T/O) or ran out of memory (M/O).
%
This can be due to the fact that directly translating a quantified formula into a quantifier-free by introducing a vector of variables for each boolean possibility can lead to exponential increase in the formula size.
%
%
\subsubsection{$\fqbf$ search encoding of the universal condition}
We will describe several constraints that encode universal condition based on QBF formulation in this section.
%
To avoid cumbersome notation, we will not explicitly write the ranges
of the indexing in the constraints.
%
$i$ and $j$ will range over nodes, i.e., from $1$ to $\nu$.
%
$m$ will range over molecules, i.e., from $1$ to $\mu$.
%
$q$ will range over edges between two nodes, i.e., from $1$ to $\pi$.
%

### 2019-04-08 papers/journal/experiments.tex
Todos till experiments done

%\externaldocument{sat-table}
%We have developed four different tools (\sattool, \smttool, \qbftool, \ourtool) for implementation of proposed encodings.
%
\noindent We have developed the {\vtstool} tool to conjecture the properties of the VTS (explained in Section 6). 
%
%
The {\vtstool} tool includes about 10,000 lines of code.
%
The tool is divided into three different blocks,
%
checking existential condition, checking the universal condition and performing synthesis on the incomplete VTS. 
%
The existential condition is subdivided into two sub-blocks, bounded model checking and constraint solving. 
%
We will refer to existential subblocks \unsure{The fonts of toolset looks different make them uniform. The reason is valid although.}as {\sattool} and {\smttool}, universal block as {\qbftool} and synthesis block as {\ourtool}.
%

@@

\unsure{The bio discussion looks pale and irrelevant!}For biological cells, the steady state condition implies that every compartment that gives a vesicle necessarily receives a vesicle too.
%
On top of this, for the case where traffic molecules are regulated in some form, every pair of compartments with a vesicle going between them, have two additional vesicle paths connecting them; where these two paths go in opposite directions.
%
Finally, when we take into account the exact manner in which SNAREs interact in real cells, we find that the biological VTS must conform to a very specific structure; any two compartments that are connected by a vesicle, must be connected by 4 vesicle paths, two of them going in the same direction, and the other two in the opposite direction. 
%
No graph results suggest that a functional VTS necessarily needs some form of regulation, where the molecules of the VTS are kept inactive in places where they might disrupt other interactions

>>>>

%\externaldocument{sat-table}
%We have developed four different tools (\sattool, \smttool, \qbftool, \ourtool) for implementation of proposed encodings.
%
\noindent We have developed the {\vtstool} tool to conjecture the properties of the VTS (explained in Section 6). 
%
%
The {\vtstool} tool includes about 10,000 lines of code.
%
The tool is divided into three different blocks,
%
checking existential condition, checking the universal condition and performing synthesis on the incomplete VTS. 
%
The existential condition is subdivided into two subblocks, bounded model checking and constraint solving. 
%
We will refer to existential subblocks as {\sattool} and {\smttool}, universal block as {\qbftool} and synthesis block as {\ourtool}.
%

@@

For biological cells, the steady state condition implies that every compartment that gives a vesicle necessarily receives a vesicle too.
%
On top of this, for the case where traffic molecules are regulated in some form, every pair of compartments with a vesicle going between them, have two additional vesicle paths connecting them; where these two paths go in opposite directions.
%
Finally, when we take into account the exact manner in which SNAREs interact in real cells, we find that the biological VTS must conform to a very specific structure; any two compartments that are connected by a vesicle, must be connected by 4 vesicle paths, two of them going in the same direction, and the other two in the opposite direction. 
%
No graph results suggest that a functional VTS necessarily needs some form of regulation, where the molecules of the VTS are kept inactive in places where they might disrupt other interactions

### 2019-04-08 papers/journal/problem.tex
Todos till experiments done

\subsection{Universal condition}
%Here we will present the QBF.
\noindent We will model the search problem for the universal condition as a quantified Boolean formula (QBF)~\cite{buning2009theory, benedetti2008qbf}, and the resultant formula is solved using a QBF solver.
%
The QBF is a generalization of the Boolean satisfiability problem in which every variable is quantified using either existential or universal quantifier.
%
The QBFs enables potentially more succinct encodings than SAT but with a higher complexity class decision problem~\cite{buning2009theory}.

>>>>

\subsection{Universal condition}
%Here we will present the QBF.
\noindent We will model the search problem for the universal condition as a quantified Boolean formula (QBF)~\cite{buning2009theory, benedetti2008qbf}, and the resultant formula is solved using a QBF solver.
%
The QBF is a generalization of the Boolean satisfiability problem in which every variable is quantified using either existential or universal quantifier.
%
The QBFs enables potentially more succinct encodings than SAT but with a higher complexity class decision problem~\cite{savitch1970relationships, stockmeyer1973word}.

### 2019-04-08 papers/journal/property.tex
Intro Dia fixed
Todos till experiments done

\noindent We analyze the model against our desired properties.
%
Since in biology there are no declared specifications or properties,
we conjecture some properties that appear to be 
%true in 
relevant in
all the known
biological systems.
%
In this paper, we choose graph connectedness to be a key property.
%
We will also seek two kinds of questions give the property.
% %
% In this paper,
% our conjecture relates graph-connectedness to a particular variation of SNARE pairing and
% regulation rules of the VTS.
% %
% We are interested in the following two type of properties of the transport graph:
\begin{enumerate}
\item {\em Existential condition:}
if there is a VTS that satisfies the connectedness property.

\item {\em Universal condition:}
  if there is a connectedness property that is satisfied by each valid VTS.
\end{enumerate}
The goal is to find the minimum graph connectivity properties for each of the condition.
% In our program, the rules VTS needs to follow 
% %
% are represented as constrained over the transport graphs (G), label on the nodes and edges and activity of those labels (determined by a Boolean function f). 
% %
% Each of these constrained functions is defined to be TRUE for a G and f: if and only if the corresponding condition holds for the given G and f. 
% %
% We use these functions to define the assertion that characterizes the corresponding condition to be checked. 
% %
% We will show in later sections how we encode these Boolean functions. 
\subsubsection{Search for existential condition} 
%
% To ensure that k-connectedness is an existential condition,
%
We need to find a $k$-connected graph that satisfies all the rules (and constraints) of the system. 
%
We also aim to find the minimum $k$. 
%
%Let's fix our conjecture: ``k-connectedness is a necessary condition for the system regulated by a Boolean function on the node and SNARE-SNARE inhibition on the edge". 
%
To find a k-connected graph we specify our property as a query for the existence
of a model for a conjunction of the formula representing stability, fusion and specific
graph connectivity constraint. 
%
% \begin{align*}
%   &\texttt{LabeledVTS} = \texttt{Stability} \, \land \, \texttt{Fusion} \land \, \texttt{MinConnectivity(k)}
%  \tag{E}\label{eq:existcond}
% \end{align*}
%
We will start with the value of $k = 1$ and check for the satisfiability of the formula.
%
In case the formula is satisfiable the procedure terminates and we report the value of $k$. 
%
If the formula is not satisfiable we increment the $k$ by $1$ and repeat the same procedure. 
%
In this way, we ensure that the reported $k$ is the minimum connectivity of the VTS that
satisfies the existential condition.
%
% Used E as edge and L_e L_n as label for node and the edge,

>>>>

\noindent %\improve{The weakest part of the paper; Need a serious rewrite!}
We analyze the model against our desired properties.
%
Since in biology there are no declared specifications or properties,
we conjecture some properties that appear to be 
%true in 
relevant in
all the known
biological systems.
%
In this paper, we choose graph connectedness to be a key property.
%
We will also seek two kinds of questions give the property.
% %
% In this paper,
% our conjecture relates graph-connectedness to a particular variation of SNARE pairing and
% regulation rules of the VTS.
% %
% We are interested in the following two type of properties of the transport graph:
\begin{enumerate}
\item {\em Existential condition}:
if there is a VTS that satisfies the connectedness property.

\item {\em Universal condition}:
  if there is a connectedness property that is satisfied by each valid VTS.
\end{enumerate}
The goal is to find the minimum graph connectivity properties for each of the condition.
% In our program, the rules VTS needs to follow 
% %
% are represented as constrained over the transport graphs (G), label on the nodes and edges and activity of those labels (determined by a Boolean function f). 
% %
% Each of these constrained functions is defined to be TRUE for a G and f: if and only if the corresponding condition holds for the given G and f. 
% %
% We use these functions to define the assertion that characterizes the corresponding condition to be checked. 
% %
% We will show in later sections how we encode these Boolean functions. 
\subsubsection{Search for existential condition} 
%
% To ensure that k-connectedness is an existential condition,
%
We need to find a $k$-connected graph that satisfies all the rules (and constraints) of the system. 
%
We also aim to find the minimum $k$. 
%
%Let's fix our conjecture: ``k-connectedness is a necessary condition for the system regulated by a Boolean function on the node and SNARE-SNARE inhibition on the edge". 
%
To find a k-connected graph we specify our property as a query for the existence
of a model for a conjunction of the formula representing stability, fusion and specific
graph connectivity constraint. 
%
% \begin{align*}
%   &\texttt{LabeledVTS} = \texttt{Stability} \, \land \, \texttt{Fusion} \land \, \texttt{MinConnectivity(k)}
%  \tag{E}\label{eq:existcond}
% \end{align*}
%
We will start with the value of $k = 1$ and check for the satisfiability of the formula.
%
In case the formula is satisfiable the procedure terminates and we report the value of $k$. 
%
If the formula is not satisfiable we increment the $k$ by $1$ and repeat the same procedure. 
%
In this way, we ensure that the reported $k$ is the minimum connectivity of the VTS that
satisfies the existential condition.
%
% Used E as edge and L_e L_n as label for node and the edge,
